Preliminary Draft

### 2021-07-29 article/draft.tex
minor udpates YT and TW code

At the video level, we start at each round with a YouTube video marked as ``False'' and we expected to have a high proportion of misinformation videos. But only {$18.4\%$} of the recommendations corresponded to $misleading$ or {\it hyper-partisan} videos.
This relatively small percentage hints towards that idea that YouTube is probably reducing the visibility of videos containing misinformation. However, when we investigated misinformation at the channel level, we found that videos belonging to channels that are not highly authoritative were being often recommended. {\color{pink} mettre cl pour channel level}. Notice that the policy of reducing the visibility of misleading content is hard to prove on YouTube in general and even harder than on Facebook and Twitter.

>>>>

At the video level, we start at each round with a YouTube video marked as ``False'' and we expected to have a high proportion of misinformation videos. But only {$18.4\%$} of the recommendations corresponded to $misleading$ or {\it hyper-partisan} videos.
This relatively small percentage hints towards that idea that YouTube is probably reducing the visibility of videos containing misinformation. However, when we investigated misinformation at the channel level, we found that videos belonging to channels that are not highly authoritative were being often recommended. {\color{pink} mettre cl pour channel level, faire allusion à ce qu'ils disent}. {\color{pink} they do not act on the channel level ... hyper partisan/ misinformation ? } Notice that the policy of reducing the visibility of misleading content is hard to prove on YouTube in general and even harder than on Facebook and Twitter.
